### 2018-12-04 Chapters/OtherHams.tex
may be crashing

\begin{equation}
\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}(t)\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}(t) \bs{S}_i \times \bs{S}_j \right\}
\end{equation}

Where we neglected the pseudodipolar interaction in favor of the DMI and where:

\begin{align*}
J_{1,ij}(t) &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
J_{2,ij}(t) &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{D}_{2,ij}(t) &= - 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)
\end{align*}

Now, a Hamiltonian with the form $\hat{H} = \sum_{\langle i,j \rangle} J_1 \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} J_2\bs{S}_i\bs{S}_j$ is known as the $J_1$-$J_2$ Heisenberg model and in a 2D honeycomb lattice it exhibits N\'eel order for $J_2 < J_1 / 6$ and for $J_2 > J_1 / 6$ spin density waves (SDW) appear \cite{Mulder2010}. However, in the presence of DMI alone there will always be SDW in the plane perpendicular to $\bs{D}$ \cite{Uchida2006}.

>>>>

\begin{equation}
\label{OtherHamsSpinModel}
\hat{H}_{\text{eff}}(t) = \sum_{\langle i,j \rangle} J_{1,ij}(t)\bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} \left\{ J_{2,ij}(t)\bs{S}_i\bs{S}_j + \bs{D}_{2,ij}(t) \bs{S}_i \times \bs{S}_j + \bs{S}_i \bs{\Gamma}_{ij}(t) \bs{S}_j \right\}
\end{equation}

\begin{align*}
J_{1,ij}(t) &= t_1^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
J_{2,ij}(t) &= t_2^2\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{D}_{2,ij}(t) &= - 2\nu_{ij} t_2 \Delta \hat{e}_z \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \\
\bs{\Gamma}_{2,ij}(t) &= \Delta^2 \text{diag}(-1,-1,1) \mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) 
\end{align*}

Now, a Hamiltonian with the form $\hat{H} = \sum_{\langle i,j \rangle} J_1 \bs{S}_i\bs{S}_j + \sum_{\langle \langle i,j \rangle \rangle} J_2\bs{S}_i\bs{S}_j$ is known as the $J_1$-$J_2$ Heisenberg model and in a 2D honeycomb lattice it exhibits N\'eel order for $J_2 < J_1 / 6$ and for $J_2 > J_1 / 6$ spin density waves (SDW) appear \cite{Mulder2010}. However, in the presence of DMI alone there will always be SDW in the plane perpendicular to $\bs{D}$ \cite{Uchida2006}. In general SDW will appear in the ground state of \ref{OtherHamsSpinModel} and the SDW wavevector will be determined by a function of the parameters of this model. Next we will show numerically that the ratio between the NN and NNN parameters can be modulated by the intensity of the field, and therefore the field can be used to control the SDW wavevector.

We will use the time average approximation \ref{MFactorApprox0} so that we can write:

\begin{align}
J_{1,ij} &= J_{1,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\alpha_{ij})^2}{1+n\frac{\omega}{\text{U}}} \\
D_{2,ij} &= D_{2,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\alpha_{ij})^2}{1+n\frac{\omega}{\text{U}}}
\end{align}

Where $J_{1,ij}^0 = \frac{2t_1^2}{\text{U}}$ and $D_{2,ij}^0 = \frac{4t_2\Delta}{\text{U}}$. Now, for circularly polarized light we have $|\alpha_{ij}| = \frac{1}{\sqrt{2}}e|\vec{R}_{ij}| \frac{E_0}{\omega} = \frac{1}{\sqrt{2}}ea \frac{E_0}{\omega} \frac{|\vec{R}_{ij}|}{a} = \frac{|\vec{R}_{ij}|}{\sqrt{2}a} \mathcal{E}$:

\begin{align}
J_{1,ij} &= J_{1,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\frac{1}{\sqrt{2}}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}} \\
D_{2,ij} &= D_{2,ij}^0  \sum_{n} \frac{\mathcal{J}_n(\sqrt{\frac{3}{2}}\mathcal{E})^2}{1+n\frac{\omega}{\text{U}}}
\end{align}

Therefore, $|\alpha_{ij}|$ will be $\sqrt{3}$ times bigger for NNN than for NN, and, in each case the absolute vale is independent of $i,j$.  Now, in units $\hbar=t_1=1$ we measure energy in units of $t_1$ and frequency in units of $\frac{t_1}{\hbar}$. Then, for $t_2 = 0.1$, $\Delta = 0.5$, $\text{U} = 10$ and $\omega = 6$ we obtain (ref fig). The ratio $\frac{J_{1,ij}}{D_{2,ij}}$ is plotted in (figure)

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{Chapters/NNvsNNN.jpg}
  \caption{A subfigure}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.4\linewidth]{Chapters/ratio.jpg}
  \caption{A subfigure}
  \label{fig:sub2}
\end{subfigure}
\caption{A figure with two subfigures}
\label{fig:test}
\end{figure}
